 \documentclass[prc,amsart,english,twocolumn,superscriptaddress,showpacs,floatfix]{revtex4}
 \usepackage[T1]{fontenc}       % DC-fonts
 \begin{document}


 \section*{Contribution from Morten Hjorth-Jensen (as of April 25 2015)}


 \subsection*{Regular Articles in Journals with a Referee System only, after March 31 2014}
 \begin{enumerate}


\item G. Hagen, A. Ekström, G. R. Jansen, W. Nazarewicz, T. Papenbrock, K. A. Wendt, B. Carlsson, C. Forssen, M. Hjorth-Jensen, S. Bacca, N. Barnea, M. Miorelli, G. Orlandini, C. Drischler, K. Hebeler, J. Simonis, A. Schwenk
\newblock {Charge, neutron, and weak size of the atomic nucleus}
\newblock {\em Science}, in preparation (2015).

\item Gustav Baardsen, Karl Leikanger, Titus Morris, Sarah Reimann, Scott Bogner, and Morten Hjorth-Jensen,
\newblock {Many-body approaches to the homogeneous electron gas in two and three dimensions}, 
\newblock {\em  Journal of Chemical Physics}, in preparation (2015).

\item Y. Fei, S. Reimann, S.~K.~Bogner and M.~Hjorth-Jensen, 
\newblock {First principle calculations of quantum dot systems},\newblock in preparation for Physical Review B (2015).

\item A.~Ekstr\"om, G. R. Jansen, K. A. Wendt, G. Hagen, T. Papenbrock, B. D. Carlsson, C. Forssen, M. Hjorth-Jensen, P. Navratil, W. Nazarewicz, 
\newblock {Accurate nuclear radii and binding energies from a chiral interaction},\newblock {\em Physical Review C}, 91:xxxx(R), in press (2015).

\item A. Ekstr\"om, B. D. Carlsson, K. A. Wendt, C. Forssen, M. Hjorth-Jensen, R. Machleidt, S. M. Wild,
\newblock {Statistical uncertainties of a chiral interaction at next-to-next-to leading order}, 
\newblock {\em Journal of Physics G}, 42:034003 (2015).


\item A.~B.~Balantekin, J.~Carlson, D.~J.~Dean, G.~M.~Fuller, R.~J.~Furnstahl, M.~Hjorth-Jensen, R.~V.~F.~Janssens, Bao-An Li, W.~Nazarewicz, F.~M.~Nunes, W.~E.~Ormand, S.~Reddy, B.~M.~Sherrill
,
\newblock {Nuclear Theory and Science of the Facility for Rare Isotope Beams}, 
\newblock {\em Modern Physics Letters A}, 29:1430010 (2014).

\item Zs. Vajta, M. Stanoiu, D. Sohler, G. R. Jansen, F. Azaiez, Zs. Dombrádi, O. Sorlin, B. A. Brown, M. Belleguic, C. Borcea, C. Bourgeois, Z. Dlouhy, Z. Elekes, Zs. Fülöp, S. Grévy, D. Guillemaud-Mueller, G. Hagen, M. Hjorth-Jensen, F. Ibrahim, A. Kerek, A. Krasznahorkay, M. Lewitowicz, S. M. Lukyanov, S. Mandal, P. Mayet, J. Mrázek, F. Negoita, Yu.-E. Penionzhkevich, Zs. Podolyák, P. Roussel-Chomaz, M. G. Saint-Laurent, H. Savajols, G. Sletten, J. Timár, C. Timis, and A. Yamamoto,

\newblock {Excited states in the neutron-rich nucleus ${}^{25}\mbox{F}$}, 
\newblock {\em Physical Review C}, 89:054323 (2014).

\item A. Sanetullaev, M.B. Tsang, W.G. Lynch, Jenny Lee, D. Bazin, K.P. Chan, D. Coupland, V. Henzl, D. Henzlova, M. Kilburn, A.M. Rogers, Z.Y. Sun, M. Youngs, R.J. Charity, L.G. Sobotka, M. Famiano, S. Hudan, D. Shapira, W.A. Peters, C. Barbieri, M. Hjorth-Jensen, M. Horoi, T. Otsuka, T. Suzuki, Y. Utsuno
\newblock {Neutron spectroscopic factors of $^{55}$Ni hole-states from (p,d) transfer reactions}, 
\newblock {\em Physics Letters B}, 736:137 (2014).

\item  T.~Papenbrock, G.~Hagen, M.~Hjorth-Jensen, and  D.~J.~Dean, 
\newblock { Coupled-cluster computations of atomic nuclei}, 
\newblock {\em Reports on Progress in Physics}, 77:096302 (2014).


\item G.~Hagen, T.~Papenbrock,   A.~Ekstr\"om, G.~Baardsen, S.~Gandolfi, K.~A.~Wendt, M.~Hjorth-Jensen, and C.~Horowitz,
\newblock { Coupled-cluster calculations of nucleonic matter}, 
\newblock {\em Physical Review C},  89:014319 (2014).



 \end{enumerate}


 \subsection*{Books}
\begin{enumerate}
\item  M.~Hjorth-Jensen, 
\newblock {\em Computational Physics: An Introduction} 
\newblock IOP Publishing, to be published Fall 2015
\item  M.~Hjorth-Jensen, 
\newblock {\em Computational Physics: An Advanced Course} 
\newblock IOP Publishing, to be published Fall 2016/Spring 2017
\item I have two more book projects, but they will not be started before the spring of 2016. 
\end{enumerate}

 \subsection*{Talks at workshops, conferences and institute seminars and organization of meetings}
\begin{enumerate}

\item
{\em Living at the edge of stability, understanding the limits of the nuclear landscape}, Institute colloquium, Department of Physics, Lousiana State University, Baton Rouge, Lousiana, April 3 2014.

\item
{\em Computing in Science education, how to introduce a computational perspective in the basic science education}, special colloquium Department of Physics, Lousiana State University, Baton Rouge, Lousiana, April 4 2014.
 
\item 
{\em Correlations in Nuclei and Quantum Dots}, invited talk at  The Fourth Conference on NUCLEI and MESOSCOPIC PHYSICS, Michigan State University, May 5-9 2015.

\item 
{\em Nuclear Talent School in Nuclear Astrophysics}, organizer of the Nuclear Talent course on Nuclear Astrophysics, 
Michigan State University, May 26 - June 13, 2014. 

\item
{\em Theory challenges around $^{78}$Ni and $^{132}$Sn}, invited talk at  RIBSS Center retreat and CSAC, Michigan State University, June 11-13 2014.


\item 
{\em Nuclear Talent course on Density Functional theories}, organizer, European Center for Theoretical Nuclear Physics and Related Areas, Trento, Italy, July 13 -August 1 2014.
\item {\em From Nuclei to Neutron Stars: Why Is Matter Stable?} Physics Colloquium, Ohio University, Athens, Ohio,  February 27 2015.

\item {\em Computing in Science Education.  Integrating a Computational Perspective in the Basic Science Education}, condensed matter seminar, Ohio University, Athens, Ohio,  February 26 2015.

\item {\em Computing in Science Education.  Integrating a Computational Perspective in the Basic Science Education}, Physics Colloquium, Central Michigan University, Mt Pleasant, March 19 2015.

\item {\em Integrating a Computational Perspective in the Basic Science Education}, Special Lectures and Events, Notre Dame University, South Bend, Indiana, March 30 2015.

\item {\em Correlations in many-body systems, from condensed matter physics to nuclear physics}, Nuclear Physics Seminar, Iowa State University, Ames, Iowa, April 22 2015.
\item {\em ​Integrating a Computational Perspective in the Basic Science Education}, Special Lectures and Events, Notre Dame University, South Bend, Indiana, March 30 2015.

\item {\em Nuclear physics education and the national FRIB theory center, plus some cool ways to organize your lectures}, special seminar, Iowa State University, Ames, Iowa, April 23 2015.

\item {\em Correlations in many-body systems, from condensed matter physics to nuclear physics}, invited talk at Clarkfest 15,  conference in honor of John W Clark, Wayman Crow Professor of Physics, Washington University in St. Louis, Missouri, April 27-28 2015.
\end{enumerate}


 \subsection*{Service to the community}

\begin{enumerate}
\item Member of the Canadian research council's evaluation board on subatomic physics 2012-2015.
\item Editorial Board member of Physical Review C 2014-2016
\item Editorial Board member of European Physical Journal A since 2010
\item Editorial Board member of European Physical Journal Special Topics since 2010
\item Editorial Board member of Springer's Lecture Notes in Physics since 2010
\item Editorial Board member of Springer's Undergraduate Lecture Notes in Physics since 2014
\item Editorial board member of Computers in Science and Discovery journal, a journal by IOP, UK since 2006. Closed in 2014.
\item Member of the steering committee for the FRIB theory center
\item Chairing the steering committee of the Nuclear Talent initiative, \url{www.nucleartalent.org}, from january 2011 till February 2015, now co-director.  
\end{enumerate}

 \subsection*{Prizes, awards and professional recognitions}
\begin{enumerate}
\item March 22 2013 I became an elected fellow of the Norwegian Academy of Science and Letters
\item Elected member of the Royal Norwegian Society of Sciences and Letters, January 2015 \\
\end{enumerate}

\subsection*{Personal Summary}

I started in January 2012 at Michigan State University. I have a
shared position between the University of Oslo and Michigan State
University.

My main activity is on studies of nuclear physics systems, with an
emphasis on many-body methods for nuclear structure studies. In
particular, I wish to understand the stability of nuclear matter and
nuclei from first principle methods. This matches perfectly the
scientific mission of the NSCL and FRIB at MSU.  Several of the
articles published in the review period address these issues, amongst
these there are several articles which study
nuclei close to the lines of stability.  Moreover, our recent
optimizitation program holds great promise for the future.  We 
started this work in 2012, and the results are extremely interesting.  We
have recently optimized the nucleon-nucleon and the three-nucleon interaction from chiral
effective field theory at next-to-next- to-leading order. These results will published soon in the Physical Review C.
The accurate reproduction of nuclear radii and binding energies is a long-standing challenge in nuclear theory. To address this problem two-nucleon and three-nucleon forces from chiral effective field theory are optimized simultaneously to low-energy nucleon-nucleon scattering data, as well as binding energies and radii of few-nucleon systems and selected isotopes of carbon and oxygen. Coupled-cluster calculations based on this interaction, named NNLOsat, yield accurate binding energies and radii of nuclei up to $^{40}$Ca, and are consistent with the empirical saturation point of symmetric nuclear matter. In addition, the low-lying collective $3^-$ states in 
$^{16}$O and $^{40}$Ca are described accurately, while spectra for selected p- and sd-shell nuclei are in good agreement with experiment.

This optimization program opens up for a nuclear theory program whose outcome can lead to a serious test of chiral perturbation theory in a nuclear many-body environment,
with proper error quantifications in  nuclear many-body context.
Applying several many-body method and  developing a strong
computational axis, the aim is to develop optimized nuclear Hamiltonians that can be used to study properties of nuclei to be studied at FRIB. 

I have also a strong educational commitment, reflected in the initiation and partecipation in a project at the University of Oslo called 'Computing in Science Education'. This project has changed totally the way we teach science, with computations being introduced at first semester of study. Many of the seminars I have given at various US institutions deal with the integration of a computational approach to the basic science courses. Only this year I have given such seminars at Ohio University, Central Michigan University, Notre Dame University and Iowa State University. I will give a similar seminar later this year at MSU as well.

I am also involved in the so-called Nuclear Talent initiative, see \url{http://nucleartalent.org} for more details. 
This year we will run three courses,  and I am organizing one of the courses, together with Wim Dickhoff from Washington University in St Louis. 
I am also a member of the teaching team of this course, which starts  on July 6 and ends after three weeks. GANIL at Caen in France is the laboratory which hosts the course.
I will also teach at the Doctoral program in Nuclear Physics at the ECT* this years, as well as at the National Nuclear Physics Summer School, this year at Lake Tahoe in California.

Locally I have extensive collaborations with fellow theorists Scott Bogner, Alex Brown, Heiko Hergert, Witek Nazarewicz and partly with Filomena Nunes, as well as tight collaborations with our graduate students and post-doctoral fellows. The Theory trailer is a lively community, with an average age well below 35. I collaborate also 
with many experimentalists at the lab. 

Finally, my long term goal is to be able to contribute to build up a
strong activity on the nuclear many-body problem at MSU, an activity
which will match the experimental program at the NSCL and FRIB. With
Scott Bogner we have now a group of seven excellent graduate students, and we will most likely recruit et another this summer.

Furthermore, since I am a member FRIB theory center sterring
committee, I hope I can contribute in building an intellectually
stimulating environment which will continue to attract excellent
students and produce great science.


 \end{document}








\item G. Baardsen, A.\ Ekstr\"om, G.\ Hagen, and M.\ Hjorth-Jensen,
\newblock { Coupled-cluster studies of infinite  nuclear matter}, 
\newblock {\em Physical Review C}, 88:054312 (2013).


\item V.\ M.\ Bader, A.\ Gade, D.\ Weisshaar, T.\ Baugher, D.\ Bazin, J.\ S.\ Berryman, B.\ A.\ Brown, A.\ Ekstr\"om, M.\ Hjorth-Jensen, S.\ R.\ Stroberg, W.\ B.\ Walters, K.\ Wimmer, and R.\ Winkler, 
\newblock { Quadrupole collectivity in neutron-deficient Sn nuclei: $^{104}$Sn and the role of proton excitations}, 
\newblock {\em Physical Review C},  88:051301(R) (2013).

\item  A.~Ekstr\"om, G. Baardsen, C.~Forss\'en, G.~Hagen, M.~Hjorth-Jensen, G.~R.~Jansen, R.~Machleidt, W.~Nazarewicz, T.~Papenbrock, J.~Sarich, and S.~M.~Wild, 
\newblock { An optimal chiral interaction at next-to-next-to leading order}, 
\newblock {\em Physical Review Letters},  110:192502 (2013).


\item Lepailleur, A. and Sorlin, O. and Caceres, L. and Bastin, B. and Borcea, C. and Borcea, R. and Brown, B. A. and Gaudefroy, L. and Gr\'evy, S. and Grinyer, G. F. and Hagen, G. and Hjorth-Jensen, M. and Jansen, G. R. and Llidoo, O. and Negoita, F. and de Oliveira, F. and Porquet, M.-G. and Rotaru, F. and Saint-Laurent, M.-G. and Sohler, D. and Stanoiu, M. and Thomas, J. C.,
\newblock { Spectroscopy of $^{26}$F to Probe Proton-Neutron Forces Close to the Drip Line}, 
\newblock {\em Physical Review Letters},  110:082502 (2013).

\item D. D. DiJulio, J. Cederkall, C. Fahlander, A. Ekstr\"om, M. Hjorth-Jensen, M. Albers, V. Bildstein, A. Blazhev, I. Darby, T. Davinson, H. De Witte, J. Diriken, Ch. Fransen, K. Geibel, R. Gernhäuser, A. Görgen, H. Hess, K. Heyde, J. Iwanicki, R. Lutter, P. Reiter, M. Scheck, M. Seidlitz, S. Siem, J. Taprogge, G. M. Tveten, J. Van de Walle, D. Voulot, N. Warr, F. Wenander, and K. Wimmer
\newblock { Coulomb excitation of $^{107}$In}, 
\newblock {\em Physical Review C},  87:017301 (2013).



\item C.~Forssen, G.~Hagen, M.~Hjorth-Jensen, W.~Nazarewicz, and J.~Rotureau,
\newblock { Living on the edge of stability, the limits of the nuclear landscape}, 
\newblock {\em Physica Scripta},  T152:014022 (2013).

\item Liddick, S. N. and Abromeit, B. and Ayres, A. and Bey, A. and Bingham, C. R. and Brown, B. A. and Cartegni, L. and Crawford, H. L. and Darby, I. G. and Grzywacz, R. and Ilyushkin, S. and Hjorth-Jensen, M. and Larson, N. and Madurga, M. and Miller, D. and Padgett, S. and Paulauskas, S. V. and Rajabali, M. M. and Rykaczewski, K. and Suchyta, S.,
\newblock { Low-energy level schemes of ${}^{\mathbf{66},\mathbf{68}}$Fe and inferred proton and neutron excitations across $\mathbf{Z}=\mathbf{28}$ and $\mathbf{N}=\mathbf{40}$}, 
\newblock {\em Physical Review C},  87:014325, 2013.


\item D. D. DiJulio, J. Cederkall, C. Fahlander, A. Ekstr\"om, M. Hjorth-Jensen, M. Albers, V. Bildstein,
A. Blazhev, I. Darby, T. Davinson, H. De Witte, J. Diriken, Ch. Fransen, K. Geibel, R. Gernh\"auser,
A. G\"orgen, H. Hess, J. Iwanicki, R. Lutter, P. Reiter, M. Scheck, M. Seidlitz, S. Siem, J. Taprogge,
G.M. Tveten, J. Van de Walle, D. Voulot, N. Warr, F. Wenander, and K. Wimmer,
\newblock { Excitation strengths in $^{109}$Sn: Single-neutron and collective excitations near $^{100}$Sn}, 
\newblock {\em Physical Review C},  86:031302(R), 2012.

\item D. D. DiJulio, J. Cederkall, C. Fahlander, A. Ekstr\"om, M. Hjorth-Jensen, M. Albers, V. Bildstein,
A. Blazhev, I. Darby, T. Davinson, H. De Witte, J. Diriken, Ch. Fransen, K. Geibel, R. Gernh\"auser,
A. G\"orgen, H. Hess, J. Iwanicki, R. Lutter, P. Reiter, M. Scheck, M. Seidlitz, S. Siem, J. Taprogge,
G.M. Tveten, J. Van de Walle, D. Voulot, N. Warr, F. Wenander, and K. Wimmer,
\newblock { Coulomb excitation of $^{107}$Sn}, 
\newblock {\em European Journal of Physics A}, 48:105,  2012.


\item
Gaute Hagen, Morten Hjorth-Jensen, Gustav Ragnar Jansen, Ruprecht Machleidt, and Thomas Papenbrock
\newblock { Evolution of shell structure in neutron-rich calcium isotopes }, 
\newblock {\em Physical Review Letters}, 109:032502, 2012.

\item
Gaute Hagen, Morten Hjorth-Jensen, Gustav Ragnar Jansen, Ruprecht Machleidt, and Thomas Papenbrock
\newblock { Continuum effects and three-nucleon forces in neutron-rich
           oxygen isotopes}, 
\newblock {\em Physical Review Letters}, 108:242501, 2012.


\item
Torres, D. A. and Kumbartzki, G. J. and Sharon, Y. Y. and Zamick,
	L. and Manning, B. and Benczer-Koller, N. and Speidel, K.-H. and
	Ahn, T. and Anagnostatou, V. and Elvers, M. and Goddard, P. and Heinz,
	A. and Ilie, G. and Radeck, D. and Savran, D. and Werner, V. and
	G\"urdal, G. and Taylor, M. J. and Maier-Komor, P. and Hjorth-Jensen,
	M. and Robinson, S. J. Q.
\newblock { Measurement of the ${}^{96}$Ru $g({4}_{1}^{+})$ factor and its nuclear
	structure interpretation}.
\newblock {\em Physical Review C}, 85:017305, 2012.


\item
Torres, D. A. and Kumbartzki, G. J. and Sharon, Y. Y. and Zamick,
	L. and Manning, B. and Benczer-Koller, N. and G\"urdal, G. and Speidel,
	K.-H. and Hjorth-Jensen, M. and Maier-Komor, P. and Robinson, S.
	J. Q. and Ahn, T. and Anagnostatou, V. and Elvers, M. and Goddard,
	P. and Heinz, A. and Ilie, G. and Radeck, D. and Savran, D. and Werner,
	V.
\newblock { First $g$-factor measurements of the ${2}_{1}^{+}$ and the ${4}_{1}^{+}$
	states of radioactive ${}^{100}$Pd}.
\newblock {\em Physical Review C}, 84:044327, 2011.


\item
Naofumi Tsunoda, Takaharu Otsuka, Koshiroh Tsukiyama, and Morten Hjorth-Jensen
\newblock { Renormalization persistency of the tensor force
           in nuclei}.
\newblock {\em Physical Review C}, 84:044322, 2011.


\item
\O yvind Jensen, Gaute Hagen, Morten Hjorth-Jensen, Alex Boyd Brown, and Alexandra Gade
\newblock { Quenching of spectroscopic factors for proton removal
           in oxygen isotopes}, 
\newblock {\em Physical Review Letters}, 107:032501, 2011.

\item
Magnus Pedersen Lohne, Gaute Hagen, Morten Hjorth-Jensen, Simen Kvaal, and Francesco Pederiva,
\newblock { Ab initio calculations of Circular quantum dots}.
\newblock {\em Physical Review B}, 84:032501, 2011.




\item
Elise Bergli and Morten Hjorth-Jensen.
\newblock { Summation of Parquet diagrams as an {\em ab initio} method in
  nuclear structure calculations}.
\newblock {\em Annals of Physics}, 326:1125, 2011.



\item
Gustav Ragnar Jansen, Morten Hjorth-Jensen, Gaute Hagen, and Thomas Papenbrock,
\newblock { Toward open-shell nuclei with coupled-cluster theory}.
\newblock {\em Physical Review C}, 83:054306, 2011.

\item
Morten Hjorth-Jensen.
\newblock { The Carbon Challenge}.
\newblock {\em Physics}, 4:38, 2011.


\item
\O{}. Jensen, G.~Hagen, M.~Hjorth-Jensen, and J.~S. Vaagen.
\newblock { Closed-shell properties of $^{24}$O with ab initio
  coupled-cluster theory}.
\newblock {\em Physical Review C}, 83:021305, 2011.

\item
Angelo Signoracci, B.~Alex Brown, and Morten Hjorth-Jensen.
\newblock { Renormalized interactions with a realistic single-particle
  basis}.
\newblock {\em Physical Review C}, 83:024315, 2011.



\item
Boyd~Alexander Brown, Angelo Signoracci, and Morten Hjorth-Jensen.
\newblock { Configuration interactions constrained by energy density
  functionals}.
\newblock {\em Physics Letters B}, 695:507, 2011.


\item
G.~Hagen, T.~Papenbrock, D.~J. Dean, and M.~Hjorth-Jensen.
\newblock Ab initio coupled-cluster approach to nuclear structure with modern
  nucleon-nucleon interactions.
\newblock {\em Phys.~Rev.~C}, 82(3):034330, 2010.


\item
L.~Atanasova, Dimiter Balabanski, S.~K. Chamoli, M.~Hass, G.~S. Simpson,
  D.~Bazzacco, F.~Becker, P.~Bednarczyk, G.~Benzoni, N.~Blasi, A.~Blazhev,
  A.~Bracco, C.~Brandau, L.~Caceres, F.~Camera, F.~C.~L. Crespi, P.~Detistov,
  P.~Doornenbal, C.~Fahlander, E.~Farnea, G.~Georgiev, J.~Gerl, K.~A.
  Gladnishki, M.~Gorska, J.~Grebosz, R.~Hoischen, G.~Ilie, M.~Ionescu-Bujor,
  A.~Iordachescu, A.~Jungclaus, G.~Bianco, M.~Kmiecik, I.~Kojouharov, N.~Kurz,
  S.~Lakshmi, R.~Lozeva, A.~Maj, D.~Montanari, G.~Neyens, M.~Pfuetzner,
  S.~Pietri, Z.~Podolyak, W.~Prokopowicz, D.~Rudolph, G.~Rusev, T.~Saito,
  A.~Saltarelli, H.~Schaffner, R.~Schwengner, S.~Tashenov, J.~J.
  Valiente-Dobon, N.~Vermeulen, J.~Walker, E.~Werner-Malento, O.~Wieland, H.~J.
  Wollersheim, H.~Grawe, and Morten Hjorth-Jensen.
\newblock { $g$-factor measurements at RISING: The cases of $^{127}$Sn and
  $^{128}$Sn}.
\newblock {\em Europhysics letters}, 91:42001, 2010.

\item
I.~Darby, R.~Grzywacz, J.~C. Batchelder, C.~R. Bingham, L.~Cartegni, C.~J.
  Gross, Morten Hjorth-Jensen, D.~T. Joss, S.~N. Liddick, W.~Nazarewicz,
  S.~Padgett, R.~D. Page, Thomas Papenbrock, M.~M. Rajabali, J.~Rotureau, and
  K.~P. Rykaczewski.
\newblock { Orbital Dependent Nucleonic Pairing in the Lightest Known
  Isotopes of Tin}.
\newblock {\em Physical Review Letters}, 105:162502, 2010.

\item
A.~Ekstr\o{}m, Joakim Cederkall, Claes Fahlander, Morten Hjorth-Jensen, Torgeir
  Engeland, Peter Butler, P.~A. Butler, T.~Davinson, J.~Eberth, F.~Finke,
  Andreas Gorgen, M.~Gorska, A.~M. Hurst, O.~Ivanov, J.~Iwanicki, U.~Koster,
  B.~A. Marsh, J.~Mierzejewski, P.~Reiter, Sunniva Siem, G.~Sletten,
  I.~Stefanescu, Gry~Merete Tveten, J.~Van~de Walle, D.~Voulot, N.~Warr,
  D.~Weisshaar, F.~Wenander, and M.~Zielinska.
\newblock { Coulomb excitation of the odd-odd isotopes $^{106}$In and
  $^{108}$In}.
\newblock {\em European Physical Journal A}, 44:355, 2010.

\item
Gaute Hagen, Thomas Papenbrock, and Morten Hjorth-Jensen.
\newblock { Ab Initio Computation of the $^{17}$F Proton Halo State and
  Resonances in $A=17$ Nuclei}.
\newblock {\em Physical Review Letters}, 104:182501, 2010.

\item
Morten Hjorth-Jensen, David~Jarvis Dean, G.~Hagen, and Simen Kvaal.
\newblock { Many-body interactions and nuclear structure}.
\newblock {\em Journal of Physics G: Nuclear and Particle Physics}, 37:064035,
  2010.

\item
N.~Hoteling, C.~Chiara, R.~Broda, W.~B. Walters, R.~V.~F. Janssens, Morten
  Hjorth-Jensen, M.~B. Carpenter, B.~Fornal, A.~A. Hecht, W.~Krolas,
  T.~Lauritsen, T.~Pawlat, D.~Seweryniak, X.~Wang, A.~Wohr, J.~Wrzesinski, and
  S.~Zhu.
\newblock { Structure of $^{60,62}$Fe and the onset of $\nu g(9/2)$
  occupancy}.
\newblock {\em Physical Review C}, 82:044305, 2010.

\item
Takahuro Otsuka, Toshio Suzuki, Micho Honma, Yutaka Utsuno, Naofumi Tsunoda,
  Koshiroh Tsukiyama, and Morten Hjorth-Jensen.
\newblock { Novel Features of Nuclear Forces and Shell Evolution in Exotic
  Nuclei}.
\newblock {\em Physical Review Letters}, 104:012501, 2010.

\item
C.~Barbieri and Morten Hjorth-Jensen.
\newblock { Quasiparticle and quasihole states of nuclei around $^{56}$Ni}.
\newblock {\em Physical Review C}, 79:064313, 2009.

\item
A.~Ekstr\o{}m, J.~Cederkall, D.~D. DiJulio, C.~Fahlander, Morten Hjorth-Jensen,
  A.~Blazhev, B.~Bruyneel, P.~A. Butler, T.~Davinson, J.~Eberth, C.~Fransen,
  K.~Geibel, H.~Hess, O.~Ivanov, J.~Iwanicki, O.~Kester, J.~Kownacki,
  U.~Koster, B.~A. Marsh, P.~reiter, M.~Scheck, B.~Siebeck, Sunniva Siem,
  I.~Stefanescu, Heidi~Kristine Toft, Gry~Merete Tveten, J.~Van~de Walle,
  D.~Voulot, N.~Warr, D.~Weisshaar, F.~Wenander, K.~Wrzosek, and M.~Zielinska.
\newblock { Electric quadrupole moments of the $2_1^+$ states in
  $^{100,102,104}$Cd}.
\newblock {\em Physical Review C}, 80:054302, 2009.

\item
G.~Hagen, T.~Papenbrock, D.~J. Dean, Morten Hjorth-Jensen, and B.~V. Asokan.
\newblock { Ab initio computation of neutron-rich oxygen isotopes}.
\newblock {\em Physical Review C}, 80:021306, 2009.

\item
Micho Honma, Takahuro Otsuka, T.~Mizusaki, and Morten Hjorth-Jensen.
\newblock { New effective interaction for $f(5)pg(9)$-shell nuclei}.
\newblock {\em Physical Review C}, 80:064323, 2009.

\item
Koshiroh Tsukiyama, Morten Hjorth-Jensen, and Gaute Hagen.
\newblock { Gamow shell-model calculations of drip-line oxygen isotopes}.
\newblock {\em Physical Review C}, 80:051301(R), 2009.

\item
David~J. Dean, Gaute Hagen, Morten Hjorth-Jensen, and Thomas Papenbrock.
\newblock { Computational aspects of nuclear coupled-cluster theory}.
\newblock {\em Computational Science and Discovery}, 1:015008, 2008.

\item
David~J. Dean, Gaute Hagen, Morten Hjorth-Jensen, Thomas Papenbrock, and Achim
  Schwenk.
\newblock { Comment on ``Ab initio study of $^{40}$Ca with an
  importance-truncated no-core shell model}.
\newblock {\em Physical Review Letters}, 101:119201, 2008.

\item
A.~Ekstr\o{}m, J.~Cederkall, C.~Fahlander, Morten Hjorth-Jensen, F.~Ames, P.~A.
  Butler, T.~Davinson, J.~Eberth, F.~Fincke, A.~Gorgen, M.~Gorska, D.~Habs,
  A.~M. Hurst, M.~Huyse, O.~Ivanov, J.~Iwanicki, O.~Kester, U.~Koster, B.~A.
  Marsh, J.~Mierzejewski, P.~Reiter, H.~Scheit, D.~Schwalm, Sunniva Siem,
  G.~Sletten, I.~Stefanescu, Gry~Merete Tveten, J.~V. de~Walle, P.~Van~Duppen,
  D.~Voulot, N.~Warr, D.~Weisshaar, F.~Wenander, and M.~Zielinska.
\newblock { $0_1^+\rightarrow 2_1^+$ transition strengths in $^{106}$Sn and
  $^{108}$Sn}.
\newblock {\em Physical Review Letters}, 101:01250, 2008.

\item
Gaute Hagen, Thomas Papenbrock, David~J. Dean, and Morten Hjorth-Jensen.
\newblock { Medium-Mass Nuclei from Chiral Nucleon-Nucleon Interactions}.
\newblock {\em Physical Review Letters}, 101:092502, 2008.

\item
N.~Hoteling, W.~B. Walters, R.~V.~F. Janssens, R.~Broda, M.~P. Carpenter,
  B.~Fornal, A.~A. Hecht, Morten Hjorth-Jensen, W.~Krolas, T.~Lauritsen,
  T.~Pawlat, D.~Seweryniak, J.~R. Stone, X.~Wang, A.~Wohr, J.~Wrzesinski, and
  S.~Zhu.
\newblock { Rotation-aligned coupling in $^{61}$Fe}.
\newblock {\em Physical Review C}, 77:044314, 2008.

\item %{Cederkall2007}
J.~Cederkall, A.~Ekstr\o{}m, C.~Fahlander, A.~M. Hurst, Morten Hjorth-Jensen,
  F.~Ames, A.~Banu, P.~A. Butler, T.~Davinson, U.~D. Pramanik, J.~Eberth,
  S.~Franchoo, G.~Georgiev, M.~Gorska, D.~Habs, M.~Huyse, O.~Ivanov,
  J.~Iwanicki, O.~Kester, U.~Koster, B.~A. Marsh, O.~Niedermaier, T.~Nilsson,
  P.~Reiter, H.~Scheit, D.~Schwalm, T.~Sieber, G.~Sletten, I.~Stefanescu, J.~V.
  de~Walle, P.~Van~Duppen, N.~Warr, D.~Weisshaar, and F.~Wenander.
\newblock {\bf Sub-barrier Coulomb excitation of $^{110}$Sn and its
  implications for the $^{100}$Sn shell closure}.
\newblock {\em Physical Review Letters}, 98:172501, 2007.

\item %{Hagen2007a}
Gaute Hagen, David~J. Dean, Morten Hjorth-Jensen, and Thomas Papenbrock.
\newblock {\bf Complex coupled-cluster approach to an ab-initio description of
  open quantum systems}.
\newblock {\em Physics Letters B}, 656:169, 2007.

\item %{Hagen2007b}
Gaute Hagen, David~J. Dean, Morten Hjorth-Jensen, Thomas Papenbrock, and Achim
  Schwenk.
\newblock {\bf Benchmark calculations for $^3$H, $^4$He, $^{16}$O, and
  $^{40}$Ca with ab initio coupled-cluster theory}.
\newblock {\em Physical Review C}, 76:044305, 2007.

\item %{Kartamychev2007}
Maxim Kartamychev, Torgeir Engeland, Morten Hjorth-Jensen, and Eivind Osnes.
\newblock {\bf Effective interactions and shell model studies of heavy tin
  isotopes}.
\newblock {\em Physical Review C}, 76:024313, 2007.

\item %{Kvaal2007}
Simen Kvaal, Morten Hjorth-Jensen, and Halvor~M\o{}ll Nilsen.
\newblock {\bf Effective interactions, large-scale diagonalization, and
  one-dimensional quantum dots}.
\newblock {\em Physical Review B}, 76:085421, 2007.

\item %{Vaman2007}
C.~Vaman, C.~Andreoiu, D.~Bazin, A.~Becerril, B.~A. Brown, C.~M. Campbell,
  A.~Chester, J.~M. Cook, D.~C. Dinca, A.~Gade, D.~Galaviz, T.~Glasmacher,
  Morten Hjorth-Jensen, M.~Horoi, D.~Miller, V.~Moeller, W.~F. Mueller,
  A.~Schiller, K.~Starosta, A.~Stolz, J.~R. Terry, A.~Volya, V.~Zelevinsky, and
  H.~Zwahlen.
\newblock {\bf $Z=50$ shell gap near $^{100}$Sn from intermediate-energy
  coulomb excitations in even-mass $^{106-112}$Sn isotopes}.
\newblock {\em Physical Review Letters}, 99:162501, 2007.

\item %{Grour2006}
Jeffrey Grour, Piotr Piecuch, Morten Hjorth-Jensen, Marta Wloch, and
  David~Jarvis Dean.
\newblock {\bf Coupled-cluster calculations for valence systems around O-16}.
\newblock {\em Physical Review C}, 74:024310, 2006.

\item %{Hagen2006}
Gaute Hagen, Morten Hjorth-Jensen, and Michel Nicolas.
\newblock {\bf Gamow shell model and realistic nucleon-nucleon interactions}.
\newblock {\em Physical Review C}, 73:064307, 2006.

\item %{Hoteling2006}
Nathan Hoteling, W.~B. Walters, R.~V.~F. Janssens, R.~Broda, M.~F. Carpenter,
  B.~Fornal, A.~A. Hecht, Morten Hjorth-Jensen, W.~Krolas, T.~Lauritzen,
  T.~Pawlat, D.~Seweryniak, X.~Wang, A.~Wohr, J.~Wrzesinski, and S.~Zhu.
\newblock {\bf Yrast structure of $^{64}$Fe}.
\newblock {\em Physical Review C}, 74:064313, 2006.

\item %{Leske2006}
J.~Leske, K.~H. Speidel, S.~Schielke, J.~Gerber, P.~Maier-Komor, Torgeir
  Engeland, and Morten Hjorth-Jensen.
\newblock {\bf Experimental $g$ factor and B(E2) value of the $4_1^+$ state in
  Coulomb-excited $^{66}$Zn compared to shell-model predictions}.
\newblock {\em Physical Review C}, 73:064305, 2006.



\item %{Banu2005}
A.~Banu, J.~Gerl, C.~Fahlander, M.~Gorska, H.~Grawe, H.~J. Wollersheim,
  E.~Caurier, Torgeir Engeland, A.~Gniady, Morten Hjorth-Jensen, F.~Nowacki,
  T.~Beck, F.~Becker, P.~Bednarczyk, M.~A. Bentley, A.~Burger, F.~Cristancho,
  G.~de~Angelis, Z.~Dombradi, P.~Doornenbal, H.~Geissel, J.~Grebosz,
  G.~Hammond, M.~Hellstrom, J.~Jolie, I.~Kojouharov, N.~Kurz, R.~Lozeva,
  S.~Mandal, N.~Marginean, S.~Muralithar, J.~Nyberg, J.~Pochodzalla,
  W.~Prokopowicz, P.~Reiter, D.~Rudolph, C.~Rusu, N.~Saito, H.~Schaffner,
  D.~Sohler, H.~Weick, C.~Wheldon, and M.~Winkler.
\newblock {\bf $^{108}$Sn studied with intermediate-energy Coulomb excitation}.
\newblock {\em Physical Review C}, 72:061305, 2005.

\item %{Brown2005}
Boyd~Alexander Brown, Nick Stone, Irena Stone, Ian Towner, and Morten
  Hjorth-Jensen.
\newblock {\bf Magnetic moments of the $2_1^+$ states around $^{132}$Sn}.
\newblock {\em Physical Review C}, 71:044317, 2005.

\item %{Ellis2005}
Paul Ellis, Torgeir Engeland, Morten Hjorth-Jensen, Maximx Kartamyshev, and
  Eivind Osnes.
\newblock {\bf Model calculation of effective three-body forces}.
\newblock {\em Physical Review C}, 71:034301, 2005.

\item %{Hagen2005b}
Gaute Hagen, Morten Hjorth-Jensen, and Jan~S. Vaagen.
\newblock {\bf Effective interaction techniques for the Gamow shell model}.
\newblock {\em Physical Review C}, 71:044314, 2005.

\item %{Leske2005}
J.~K. Leske, Karl-heinz Speidel, S.~Schielke, J.~Gerber, P.~Maier-komor, Morten
  Hjorth-Jensen, and Torgeir Engeland.
\newblock {\bf Dominant $g_{9/2}-2$-neutron configuration in the $4^+$ state of
  $^{68}$Zn based on new $g$-factor measurements}.
\newblock {\em Physical Review C}, 72:044301, 2005.

\item %{Nilsen2005}
Jon~Kristian Nilsen, Jordi Mur-Petit, Muntsa Guilleumas, Morten Hjorth-Jensen,
  and Artur Polls.
\newblock {\bf Vortices in atomic Bose-Einstein condensates in the
  large-gas-parameter region}.
\newblock {\em Physical Review A}, 71:053610, 2005.

\item %{Sohler2005}
D.~Sohler, M.~Palacz, Z.~Dombradi, Morten Hjorth-Jensen, C.~Fahlander, L.~O.
  Norlin, J.~Nyberg, T.~Back, K.~Lagergren, D.~Rudolph, A.~Algora, C.~Andreoiu,
  G.~de~Angelis, A.~Atac, D.~Bazzacco, J.~Cederkall, B.~Cederwall, B.~Fant,
  E.~Farnea, A.~Gadea, M.~Gorska, H.~Grawe, N.~Hashimito-Saitoh, A.~Johnson,
  A.~Kerek, W.~Klamra, J.~Kownacki, S.~M. Lenzi, A.~Likar, M.~Lipoglavsek,
  M.~Moszynski, D.~R. Napoli, C.~Rossi-Alvarez, H.~A. Roth, T.~Saitoh,
  D.~Seweryniak, O.~Skeppstedt, J.~Timar, M.~Weisflog, and M.~Wolinska.
\newblock {\bf Maximally aligned states in the proton drip line nucleus
  $^{106}$Sb}.
\newblock {\em Nuclear Physics A}, 753:251, 2005.

\item %{Wloch2005a}
Marta Wloch, David~J. Dean, Jeffrey Grour, Morten Hjorth-Jensen, Karol
  Kowalski, Thomas Papenbrock, and Piotr Piecuch.
\newblock {\bf Ab-initio coupled-cluster study of $^{16}$O}.
\newblock {\em Physical Review Letters}, 94:212501, 2005.

\item %{Dean2004a}
David~J. Dean, Torgeir Engeland, Morten Hjorth-Jensen, Maxim Kartamychev, and
  Eivind Osnes.
\newblock {\bf Effective interactions and the nuclear shell-model}.
\newblock {\em Progress in Particle and Nuclear Physics}, 53:419, 2004.

\item %{Gausemel2004}
Haavar Gausemel, Birger Fogelberg, Torgeir Engeland, Morten Hjorth-Jensen,
  Per Hoff, Hendryk Mach, K.~A. Mezilev, and Jon~Petter Omtvedt.
\newblock {\bf Decay of $^{127}$In and $^{129}$In}.
\newblock {\em Physical Review C}, 69:054307, 2004.

\item %{Hagen2004}
Gaute Hagen, Jan~S. Vaagen, and Morten Hjorth-Jensen.
\newblock {\bf The contour deformation method in momentum space, applied to
  subatomic physics}.
\newblock {\em Journal of Physics A: Mathematical and General}, 37:8991, 2004.

\item %{Kowalski2004}
Karol Kowalski, David~J. Dean, Morten Hjorth-Jensen, Thomas Papenbrock, and
  Piotr Piecuch.
\newblock {\bf Coupled cluster calculations of ground and excited states of
  nuclei}.
\newblock {\em Physical Review Letters}, 92:132501, 2004.

\item %{Dean2003a}
David~J. Dean and Morten Hjorth-Jensen.
\newblock {\bf Pairing in nuclear systems: from neutron stars to finite
  nuclei}.
\newblock {\em Reviews of Modern Physics}, 75:607, 2003.

\item %{Dillmann2003}
I.~Dillmann, K.~L. Kratz, A.~Wohr, O.~Arndt, B.~A. Brown, Per Hoff, Morten
  Hjorth-Jensen, U.~Koster, A.~Ostrowski, B.~Pfeiffer, D.~Seweryniak,
  J.~Shergur, and W.~B. Walters.
\newblock {\bf $N=82$ shell-quenching of the classical r-process
  ``waiting-point'' $^{130}$Cd}.
\newblock {\em Physical Review Letters}, 91:162503, 2003.

\item %{Guttormsen2003}
Magne Guttormsen, Rositsa Chankova, Morten Hjorth-Jensen, John~Bernhard
  Rekstad, Sunniva Siem, Andreas Schiller, and David~J. Dean.
\newblock {\bf Free energy and criticality in the nucleon pair breaking
  process}.
\newblock {\em Physical Review C}, 68:034311, 2003.

\item %{Schiller2003}
A.~Schiller, Emel Algin, Lee Bernstein, P.~E. Garrett, Magne Guttormsen, Morten
  Hjorth-Jensen, C.~W. Johnson, Gary Mitchell, John~Bernhard Rekstad, Sunniva
  Siem, Alexander Voinov, and William Younes.
\newblock {\bf Level densities in $^{56,57}$Fe and $^{96,97}$Mo}.
\newblock {\em Physical Review C}, 68:054326, 2003.

\item %{Fotiades2002}
N.~Fotiades, J.~A. Cizewski, J.~A. Becker, A.~Bernstein, D.~P. Mcnabb, William
  Younes, R.~M. Clark, P.~Fallon, I.~Y. Lee, A.~O. Macchiavelli, Anne Holt, and
  Morten Hjorth-Jensen.
\newblock {\bf High-spin excitations in $^{92,93,94,95}$Zr}.
\newblock {\em Physical Review C}, 65:044303, 2002.

\item %{Lipoglavsek2002a}
M.~Lipoglavsek, C.~Baktash, Jan Blomqvist, David~J. Dean, Torgeir Engeland,
  C.~Fahlander, Morten Hjorth-Jensen, Robert V.~F. Janssens, A.~Likar, Eivind
  Osnes, and S.~D. Paul.
\newblock {\bf Break-up of the Doubly-magic $^{100}$Sn core}.
\newblock {\em Physical Review C}, 66:011302, 2002.

\item %{Lipoglavsek2002b}
M.~Lipoglavsek, C.~Baktash, M.~P. Carpenter, David~J. Dean, Torgeir Engeland,
  C.~Fahlander, Morten Hjorth-Jensen, and Eivind Osnes.
\newblock {\bf Excited states of the proton emitter $^{105}$Sb}.
\newblock {\em Physical Review C}, 65:051037, 2002.

\item %{Lipoglavsek2002c}
M.~Lipoglavsek, C.~Baktash, M.~P. Carpenter, David~J. Dean, Torgeir Engeland,
  Morten Hjorth-Jensen, and Eivind Osnes.
\newblock {\bf Core excitations in $^{102}$In}.
\newblock {\em Physical Review C}, 65:021302(R), 2002.

\item %{Ressler2002}
J.~J. Ressler, W.~B. Walters, C.~N. Davids, David~J. Dean, Andreas Heinz,
  Morten Hjorth-Jensen, D.~Seweryniak, and J.~Shergur.
\newblock {\bf First observation of $^{109}$Te $\beta^+$ and electron capture
  decay of $^{109}$Sb}.
\newblock {\em Physical Review C}, 66:024308, 2002.

\item %{Schiller2002}
Andreas Schiller, Magne Guttormsen, Morten Hjorth-Jensen, John~Bernhard
  Rekstad, and Sunniva Siem.
\newblock {\bf Model for pairing phase transition in atomic nuclei}.
\newblock {\em Physical Review C}, page 024315, 2002.

\item %{Shergur2002b}
J.~Shergur, B.~A. Brown, V.~N. Fedosseev, U.~K?ster, K.~L. Kratz,
  D.~Seweryniak, W.~B. Walters, A.~Wohr, D.~Fedorov, M.~Hannawald, Morten
  Hjorth-Jensen, V.~Mishin, B.~Pfeiffer, J.~J. Ressler, H.~O.~U. Fynbo, and Per
  Hoff.
\newblock {\bf Beta decay studies of $^{135-137}$Sn using selective reonace
  laser ionization techniques}.
\newblock {\em Physical Review C}, 65:034313, 2002.

\item %{Guttormsen2001}
Magne Guttormsen, Morten Hjorth-Jensen, Elin Melby, John~Bernhard Rekstad,
  Andreas Schiller, and Sunniva Siem.
\newblock {\bf Heat capacity and pairing transition in nuclei}.
\newblock {\em Physical Review C}, 64:034319, 2001.

\item %{Schiller2001a}
Andreas Schiller, Amund Bjerve, Magne Guttormsen, Morten Hjorth-Jensen, Finn
  Ingebretsen, Elin Melby, John~Bernhard Rekstad, Sunniva Siem, and
  Stein~Westad \O~deg\aa rd.
\newblock {\bf The critical temperature for quenching of pair correlations}.
\newblock {\em Physical Review C}, 63:021306, 2001.

\item %{Siiskonen2001}
Teemu Siiskonen, Morten Hjorth-Jensen, and Jouni Suhonen.
\newblock {\bf Renormalization of the weak hadronic current in the nuclear
  medium}.
\newblock {\em Physical Review C}, 63:024315, 2001.

\item %{Engeland2000}
Torgeir Engeland, Morten Hjorth-Jensen, and Eivind Osnes.
\newblock {\bf Shell model studies of the proton drip line nucleus $^{106}$Sb}.
\newblock {\em Physical Review C}, 61:00010(R), 2000.

\item %{Guttormsen2000a}
Magne Guttormsen, Amund Bjerve, Morten Hjorth-Jensen, Elin Melby, John~Bernhard
  Rekstad, Andreas Schiller, Sunniva Siem, and Alexandar Belic.
\newblock {\bf Entropy in hot $^{161,162}$Dy and $^{171,172}$Yb nuclei}.
\newblock {\em Physical Review C}, C62:024306, 2000.

\item %{Guttormsen2000b}
Magne Guttormsen, Morten Hjorth-Jensen, Elin Melby, John~Bernhard Rekstad,
  Andreas Schiller, and Sunniva Siem.
\newblock {\bf Energy shifted level density in the rare earth region}.
\newblock {\em Physical Review C}, 61:067302, 2000.

\item %{Guttormsen2000c}
Magne Guttormsen, Morten Hjorth-Jensen, Elin Melby, John~Bernhard Rekstad,
  Andreas Schiller, and Sunniva Siem.
\newblock {\bf Entropy of thermally excited particles in nuclei}.
\newblock {\em Physical Review C}, 63:024315, 2000.

\item %{Heiselberg2000}
Henning Heiselberg and Morten Hjorth-Jensen.
\newblock {\bf Phases of dense matter in neutron stars}.
\newblock {\em Physics Reports}, 328:237, 2000.

\item %{Holt2000}
Anne Holt, Torgeir Engeland, Morten Hjorth-Jensen, and Eivind Osnes.
\newblock {\bf Applications of realistic effective interactions to the
  structure of Zr isotopes}.
\newblock {\em Physical Review C}, 61:024315, 2000.

\item %{PhysRevC.62.067305}
M.~Tomaselli, M.~Hjorth-Jensen, S.~Fritzsche, P.~Egelhof, S.~R. Neumaier,
  M.~Mutterer, T.~Kuhl, A.~Dax, and H.~Wang.
\newblock {\bf Matter and charge distributions of $^{6}$He and $^{5,6,7,9}$Li
  within the dynamic-correlation model}.
\newblock {\em Physical Review C}, 62:067305, 2000.

\item %{Vidanya2000a}
Isaac Vidanya, Artur Polls, Angels Ramos, Lars Engvik, and Morten
  Hjorth-Jensen.
\newblock {\bf Properties of $\beta$-stable neutron star matter with hyperons}.
\newblock {\em Physical Review C}, 62:024315, 2000.

\item %{Vidanya2000b}
Isaac Vidanya, Artur Polls, Angels Ramos, Morten Hjorth-Jensen, and V.~G.~J.
  Stoks.
\newblock {\bf Strange nuclear matter within the Brueckner-Hartree-Fock
  theory}.
\newblock {\em Physical Review C}, 61:024315, 2000.

\item %{Dean1999}
David~J. Dean, M.~T. Ressell, Morten Hjorth-Jensen, S.~E. Koonin, K.~Langanke,
  and A.~P. Zuker.
\newblock {\bf Shell model Monte Carlo studies of neutron-rich nuclei in the
  $1s0d-1p0f$ shells}.
\newblock {\em Physical Review C}, 59:2474, 1999.

\item %{Heiselberg1999}
Henning Heiselberg and Morten Hjorth-Jensen.
\newblock {\bf Phase transitions in neutron stars and maximum masses}.
\newblock {\em Astrophysical Journal Letters}, 525:L45, 1999.

\item %{PhysRevC.60.064308}
S.~M. Vincent, P.~H. Regan, S.~Mohammadi, D.~Blumenthal, M.~Carpenter, C.~N.
  Davids, W.~Gelletly, S.~S. Ghugre, D.~J. Henderson, R.~V.~F. Janssens,
  M.~Hjorth-Jensen, B.~Kharraja, C.~J. Lister, C.~J. Pearson, D.~Seweryniak,
  J.~Schwartz, J.~Simpson, and D.~D. Warner.
\newblock {\bf Near yrast study of the $fpg$ shell nuclei $^{58}Ni,$ $^{61}Cu$,
  and $^{61}Zn$ }.
\newblock {\em Physical Review C}, 60:064308, 1999.

\item %{Melby1999}
Elin Melby, Lisbeth Bergholt, Magne Guttormsen, Morten Hjorth-Jensen, Finn
  Ingebretsen, Svein Messelt, John~Bernhard Rekstad, Andreas Schiller, Sunniva
  Siem, and Stein~Westad \O~deg\aa rd.
\newblock {\bf Observation of thermodynamical properties in the $^{162}$Dy,
  $^{166}$Er, $^{172}$Yb nuclei}.
\newblock {\em Physical Review Letters}, 83:3150, 1999.

\item %{Siiskonen1999a}
Teemu Siiskonen, Jouni Suhonen, and Morten Hjorth-Jensen.
\newblock {\bf Shell-model effective operators for muon capture in $^{20}$Ne}.
\newblock {\em Journal of Physics G: Nuclear and Particle Physics}, 25:L55,
  1999.

\item %{Siiskonen1999b}
Teemu Siiskonen, Jouni Suhonen, and Morten Hjorth-Jensen.
\newblock {\bf Towards the solution of the $C_P/C_A$ anomaly in shell-model
  calculations of muon capture}.
\newblock {\em Physical Review C}, 59:R1839, 1999.

\item %{Baldo1998}
Marcello Baldo, \O{}ystein Elgar\o{}y, Lars Engvik, Morten Hjorth-Jensen, and
  Hans-Josef Schulze.
\newblock {\bf Modern nucleon-nucleon potentials and $^3P_2$--$^3F_2$ pairing
  in neutron matter}.
\newblock {\em Physical Review C}, 58:1921, 1998.

\item %{Elgar孳1998a}
\O{}ystein Elgar\o{}y, Lars Engvik, Morten Hjorth-Jensen, and Eivind Osnes.
\newblock {\bf Minimal relativity and $^3S_1$--$^3D_1$ pairing in symmetric
  nuclear matter}.
\newblock {\em Physical Review C}, 57:1069, 1998.

\item %{Elgar孳1998b}
\O{}ystein Elgar\o{}y and Morten Hjorth-Jensen.
\newblock {\bf Nucleon-nucleon phase shifts and pairing in infinite matter}.
\newblock {\em Physical Review C}, 57:1174, 1998.

\item %{Grzywacz1998}
R.~Grzywacz, R.~Beraud, C.~Borcea, A.~Ensallem, M.~Glogowski, H.~Grawe,
  D.~Guillemaud-Mueller, Morten Hjorth-Jensen, M.~Houry, M.~Lewitowicz, A.~C.
  Mueller, A.~Nowak, and A.~Plochocki.
\newblock {\bf New island of $\mu s$-isomers in neutron-rich nuclei around the
  $Z=28$ and $N=40$ shell closures}.
\newblock {\em Physical Review Letters}, 81:766, 1998.

\item %{Heiselberg1998}
Henning Heiselberg and Morten Hjorth-Jensen.
\newblock {\bf Phase transitions in rotating neutron stars}.
\newblock {\em Physical Review Letters}, 80:5485, 1998.

\item %{Holt1998}
Anne Holt, Torgeir Engeland, Morten Hjorth-Jensen, and Eivind Osnes.
\newblock {\bf Shell-model calculations of heavy Sn isotopes}.
\newblock {\em Nuclear Physics A}, 634:41, 1998.

\item %{Polls1998}
Artur Polls, Herbert Muther, Ruprecht Machleidt, and Morten Hjorth-Jensen.
\newblock {\bf Phaseshift equivalent $NN$ potentials and the deuteron}.
\newblock {\em Physics Letters B}, 432:1, 1998.

\item %{Suhonen1998}
Jouni Suhonen, Jussi Toivanen, Torgeir Engeland, Morten Hjorth-Jensen, Anne
  Holt, and Eivind Osnes.
\newblock {\bf Study of odd-mass $N=82$ isotones: comparison of the microscopic
  quasiparticle-phonon model and the nuclear shell model}.
\newblock {\em Nuclear Physics A}, 628:41, 1998.

\item %{Vidanya1998}
Isaac Vidanya, Artur Polls, Angels Ramos, and Morten Hjorth-Jensen.
\newblock {\bf Hyperon properties in finite nuclei using realistic $YN$
  interactions}.
\newblock {\em Nuclear Physics A}, 644:201, 1998.

\item %{White1998}
G.~N. White, N.~J. Stone, J.~Rikovska, Y.~Koh, J.~Copell, T.~J. Giles, I.~S.
  Towner, B.~A. Brown, S.~Ohya, Birger Fogelberg, L.~Jacobsson, P.~Rahkila, and
  Morten Hjorth-Jensen.
\newblock {\bf Ground state magnetic dipole moment of $^{135}$I}.
\newblock {\em Nuclear Physics A}, 644:277, 1998.

\item %{Blasio1997}
Fabio V.~de Blasio, Morten Hjorth-Jensen, \O{}ystein Elgar\o{}y, Lars Engvik,
  Gianluca Lazzari, Marcello Baldo, and Hans-Josef Schulze.
\newblock {\bf Coherence lengths of neutron superfluids}.
\newblock {\em Physical Review C}, 56:2332, 1997.

\item %{Engvik1997a}
Lars Engvik, Morten Hjorth-Jensen, Ruprecht Machleidt, Herbert Muther, and
  Artur Polls.
\newblock {\bf Modern nucleon-nucleon potentials and symmetry energy in
  infinite matter}.
\newblock {\em Nuclear Physics A}, 627:85, 1997.

\item %{Engvik1997b}
Lars Engvik, Morten Hjorth-Jensen, Ruprecht Machleidt, Herbert Muther, and
  Artur Polls.
\newblock {\bf Modern nucleon-nucleon potentials and symmetry energy in
  infinite matter}.
\newblock {\em Nuclear Physics A}, 627:85, 1997.

\item %{Engvik1997c}
Lars Engvik, Morten Hjorth-Jensen, Eivind Osnes, and T.~Kuo.
\newblock {\bf Ring-diagram calculations of nuclear matter with different model
  spaces}.
\newblock {\em Nuclear Physics A}, 622:553, 1997.

\item %{Holt1997}
Anne Holt, Torgeir Engeland, Morten Hjorth-Jensen, Eivind Osnes, and Jouni
  Suhonen.
\newblock {\bf The structure of the $N=82$ isotones with realistic effective
  interactions}.
\newblock {\em Nuclear Physics A}, 618:107, 1997.

\item %{Sandulescu1997}
N.~Sandulescu, Roberto Liotta, Jan Blomqvist, Torgeir Engeland, Morten
  Hjorth-Jensen, Anne Holt, and Eivind Osnes.
\newblock {\bf Generalized seniority scheme in light tin isotopes}.
\newblock {\em Physical Review C}, 55:2708, 1997.

\item %{art1996i}
Lars Engvik, Morten Hjorth-Jensen, Eivind Osnes, G.~Bao, and Erlend Ostgaard.
\newblock {\bf Asymmetric Nuclear Matter and Neutron Star Properties}.
\newblock {\em Astrophysical Journal}, 469:794, 1996.

\item %{art1996h}
Alessandro Drago, Umberto Tambini, and Morten Hjorth-Jensen.
\newblock {\bf Massive quarks in neutron stars}.
\newblock {\em Physics Letters B}, 380:13, 1996.

\item %{art1996g}
\O{}ystein Elgar\o{}y, Lars Engvik, Morten Hjorth-Jensen, and Eivind Osnes.
\newblock {\bf Model-space approach to $^1S_0$ neutron and proton pairing in
  neutron star matter with the Bonn meson-exchange potentials}.
\newblock {\em Nuclear Physics A}, 604:466, 1996.

\item %{art1996f}
\O{}ystein Elgar\o{}y, Lars Engvik, Morten Hjorth-Jensen, and Eivind Osnes.
\newblock {\bf Superfluidity in $\beta$-stable neutron star matter}.
\newblock {\em Physical Review Letters}, 77:1428, 1996.

\item %{art1996e}
\O{}ystein Elgar\o{}y, Lars Engvik, Morten Hjorth-Jensen, and Eivind Osnes.
\newblock {\bf Triplet pairing of neutrons in $\beta$-stable neutron star
  matter}.
\newblock {\em Nuclear Physics A}, 607:425, 1996.

\item %{art1996d}
\O{}ystein Elgar\o{}y, Lars Engvik, Eivind Osnes, Fabio V.~de Blasio, Gianluca
  Lazzari, and Morten Hjorth-Jensen.
\newblock {\bf Emissivities of neutrinos in neutron stars}.
\newblock {\em Physical Review Letters}, 76:1994, 1996.

\item %{art1996c}
\O{}ystein Elgar\o{}y, Lars Engvik, Eivind Osnes, Fabio V.~de Blasio, Gianluca
  Lazzari, and Morten Hjorth-Jensen.
\newblock {\bf Superfluidity and neutron star crust matter}.
\newblock {\em Physical Review D. Particles and fields}, 54:1848, 1996.

\item %{art1996b}
Morten Hjorth-Jensen, Herbert Muther, Artur Polls, and Angels Ramos.
\newblock {\bf Self-energy of $\Lambda$ in finite nuclei}.
\newblock {\em Nuclear Physics A}, 605:458, 1996.

\item %{art1996a}
Morten Hjorth-Jensen, Eivind Osnes, Herbert Muther, and Artur Polls.
\newblock {\bf Comparison of the effective interaction to various orders in
  different mass regions}.
\newblock {\em Journal of Physics G: Nuclear and Particle Physics}, 22:321,
  1996.

\item %{art1995a}
Morten Hjorth-Jensen, T.~Kuo, and Eivind Osnes.
\newblock {\bf Realistic effective interactions for nuclear systems}.
\newblock {\em Physics Reports}, 261:125, 1995.

\item %{art1994d}
G.~Bao, Lars Engvik, Morten Hjorth-Jensen, Eivind Osnes, and Erlend Ostgaard.
\newblock {\bf New equations of state for neutron stars}.
\newblock {\em Nuclear Physics A}, 575:707, 1994.

\item %{art1994c}
P.~J. Ellis, Torgeir Engeland, Morten Hjorth-Jensen, Anne Holt, and Eivind
  Osnes.
\newblock {\bf Convergence properties of the effective interaction}.
\newblock {\em Nuclear Physics A}, 573:216, 1994.

\item %{art1994b}
Lars Engvik, Morten Hjorth-Jensen, Eivind Osnes, G.~Bao, and Erlend ostgaard.
\newblock {\bf Asymmetric nuclear matter and neutron star properties}.
\newblock {\em Physical Review Letters}, 73:2650, 1994.

\item %{art1994a}
Morten Hjorth-Jensen, Herbert Muther, and Artur Polls.
\newblock {\bf Width of the $\Delta$ resonance in nuclei}.
\newblock {\em Physical Review C}, 50:501, 1994.

\item %{art1993c}
Torgeir Engeland, Morten Hjorth-Jensen, Anne Holt, and Eivind Osnes.
\newblock {\bf The structure of the neutron deficient Sn isotopes}.
\newblock {\em Physical Review C}, 48:R535, 1993.

\item %{art1993b}
Morten Hjorth-Jensen, Marcello Borromeo, Herbert Muther, and Artur Polls.
\newblock {\bf Isobar contributions to the imaginary part of the optical-model
  potential for finite nuclei}.
\newblock {\em Nuclear Physics A}, 551:580, 1993.

\item %{art1993a}
Morten Hjorth-Jensen, Mariana Kirchbach, Dan~Olof Riska, and Kazuo Tsushima.
\newblock {\bf Nuclear renormalization of the isoscalar axial coupling
  constants}.
\newblock {\em Nuclear Physics A}, 563:525, 1993.

\item %{art1992c}
Morten Hjorth-Jensen, Torgeir Engeland, Anne Holt, and Eivind Osnes.
\newblock {\bf Effective interactions for valence-hole nuclei with modern
  meson-exchange potential models}.
\newblock {\em Nuclear Physics A}, 541:105, 1992.

\item %{art1992b}
Morten Hjorth-Jensen, Eivind Osnes, and T.~Kuo.
\newblock {\bf Effective interactions for valence-hole nuclei with modern
  meson-exchange potential models}.
\newblock {\em Nuclear Physics A}, 540:145, 1992.

\item %{art1992a}
Morten Hjorth-Jensen, Eivind Osnes, and Herbert Muther.
\newblock {\bf Folded-Diagram effective interaction with the Bonn
  meson-exchange potential model}.
\newblock {\em Annals of Physics}, 213:102, 1992.

\item %{art1990c}
Morten Hjorth-Jensen and Kjell Aashamar.
\newblock {\bf Oscillator strengths and lifetimes for low-lying terms in the Al
  isoelectronic sequence}.
\newblock {\em Physica Scripta}, 42:309, 1990.

\item %{art1990b}
Morten Hjorth-Jensen and Eivind Osnes.
\newblock {\bf Number-conserving sets and effective interactions through third
  order for mass-18 with the Bonn potential}.
\newblock {\em Physica Scripta}, 41:207, 1990.

\item %{art1990a}
Morten Hjorth-Jensen, Eivind Osnes, Herbert Muther, and K.~W. Schmid.
\newblock {\bf Choice of single-particle potential and the convergence of the
  effective interaction}.
\newblock {\em Physics Letters B}, 248:243, 1990.

\item %{art1989a}
Morten Hjorth-Jensen and Eivind Osnes.
\newblock {\bf Effective interactions through third order for mass-18 nuclei
  with the Paris potential}.
\newblock {\em Physics Letters B}, 228:281, 1989.


\end{numberedlist}
%\end{flushleft}

